Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2020-12-08 manuscript/draft_rsfmri.Rmd
implemented post-hoc analysis exclusion criterion 10% of data points with worst FD; ordering of df/ design matrix; "Extra analysis" moved to draft_rsfmri.Rmd

# [ ] include exclusion criteria according to "create_sample_df.R"
# [ ] Evaluate SPM model comparison (more activation in SPM..)
# [ ] Discussion
# [ ] hervorheben, was von Präregistrierung abweicht
# [ ] brain images mit nilearn plotting tools einbinden
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines

@@

```{r expample plots, eval=FALSE}
# example plots for interaction effect (arbitrary variables for illustration purposes)
ggplot(final, aes(x=tp, y=BMI, group=condition, color=condition)) +
  #geom_smooth(aes(group=condition)) +
  stat_summary(fun = mean, geom = "point", size=3, shape=15) +
  stat_summary(fun = mean, geom = "line", size=1) +
  #scale_color_brewer(values = "Set1") +
  scale_x_discrete(labels=c("bl"= "0", "fu"= "6", "fu2" = "12")) +
  scale_color_manual(values=c("#00305E","#C00045"),labels = c("intervention", "control")) +
  xlab("Time after intervention [months]") + ylab ("BMI [kg/m²]") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10), axis.title = element_text(size = 12),
    strip.text = element_text(size = 12), legend.text = element_text(size = 10),
    legend.position = "bottom", legend.background = element_rect(colour = "grey"))

>>>>

# [ ] include exclusion criteria according to "create_sample_df.R"
# [ ] Evaluate SPM model comparison (more activation in SPM..)
# [ ] Discussion
# [ ] hervorheben, was von Präregistrierung abweicht
# [ ] brain images mit nilearn plotting tools einbinden
# [ ] Upload auf Neurovolt, cf. cobidas reporting guidelines
# [ ] redo analysis with new sample 
# [ ] repeat analysis with exclusion of 10% of worst data

@@

```{r expample plots, eval=FALSE}

df_wide <- tidyr::pivot_wider(
  data = final,
  id_cols = "subj.ID",
  names_from = "tp",
  values_from = c("tp", "BMI", "logmFD")
)

if (tp == "BLFU") {
  s = 2
} else {
  s = 1
}

BMI_vector <- c("BMI_fu2", "BMI_fu", "BMI_bl")
BMI_vector <- c("BMI_bl", "BMI_fu", "BMI_fu2")
FD_vector <- c("logmFD_fu2", "logmFD_fu", "logmFD_bl")
df_wide$avgBMI <- apply(df_wide[, BMI_vector[s:3]],
                        MARGIN = 1,
                        FUN = mean,
                        na.rm = TRUE)
df_wide$avgFD <- apply(df_wide[, FD_vector[s:3]],
                       MARGIN = 1,
                       FUN = mean,
                       na.rm = TRUE)
df_long <- tidyr::pivot_longer(
  data = df_wide,
  cols = all_of(order_vector),
  # bl, fu, fu2 (maintain original order)
  # CAREFUL: Order according to dataframe df
  names_to = "tp_tp",
  values_to = "tp",
  values_drop_na = TRUE
)
all(df_long$tp == final$tp) # check if order correct

head(final[, c("subj.ID", "tp")])
head(df_long[, c("subj.ID", "tp")])

df_long$cgnBMI <- final$BMI - df_long$avgBMI
df_long$avgBMIc <-
  df_long$avgBMI - mean(df_long$avgBMI, na.rm = TRUE)
df$avgBMIc <- df_long$avgBMIc
df$cgnBMI <- df_long$cgnBMI

df_long$cgnFD <- final$logmFD - df_long$avgFD
df_long$avgFDc <-
  df_long$avgFD - mean(df_long$avgFD, na.rm = TRUE)
final$avgFDc <- df_long$avgFDc
final$cgnFD <- df_long$cgnFD

# example plots for interaction effect (arbitrary variables for illustration purposes)
ggplot(final, aes(x=tp, y=BMI, group=condition, color=condition)) +
  #geom_smooth(aes(group=condition)) +
  stat_summary(fun = mean, geom = "point", size=3, shape=15) +
  stat_summary(fun = mean, geom = "line", size=1) +
  #scale_color_brewer(values = "Set1") +
  scale_x_discrete(labels=c("bl"= "0", "fu"= "6", "fu2" = "12")) +
  scale_color_manual(values=c("#00305E","#C00045"),labels = c("intervention", "control")) +
  xlab("Time after intervention [months]") + ylab ("BMI [kg/m²]") +
  theme_bw() +  theme(
    axis.text = element_text(size = 10), axis.title = element_text(size = 12),
    strip.text = element_text(size = 12), legend.text = element_text(size = 10),
    legend.position = "bottom", legend.background = element_rect(colour = "grey"))
